---
title: "Getting Started with pgatouR"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  purl = FALSE
)
```

pgatouR gives you access to the PGA Tour's data through a clean set of R functions. Almost every function returns a tibble, so the data is immediately ready for analysis with dplyr, ggplot2, or whatever you prefer.

This article walks through the main use cases — live scoring, fields, course stats, player research, standings, and betting markets.

## Installation

```{r install}
devtools::install_github("WalrusQuant/pgatouR")
```

```{r load}
library(pgatouR)
```

## Tournament IDs

Most functions need a tournament ID. These follow the format `{tour_code}{year}{number}`:

- `"R2026027"` — 2026 FedEx St. Jude Championship (PGA Tour)
- `"R2026475"` — 2026 Valspar Championship (PGA Tour)
- `"Y2026018"` — A PGA Tour Americas event

For this week, skip the guesswork:

```{r current-event}
tid <- pga_current_tournament()$tournament_id
tid
#> [1] "R2026027"

# Champions, Korn Ferry, and Americas have their own featured events
pga_current_tournament("Y")
```

A full season list lives on `pga_schedule()`:

```{r schedule-ids}
pga_schedule(2026)
#> # A tibble: 49 × 15
#>    tournament_id tournament_name       display_date status    purse     ...
#>    <chr>         <chr>                 <chr>        <chr>     <chr>     ...
#>  1 R2026006      Sony Open in Hawaii   Jan 15 - 18  COMPLETED $9,100,000
#>  2 R2026002      The American Express  Jan 22 - 25  COMPLETED $9,200,000
#>  3 R2026004      Farmers Insurance Op… Jan 29 - F…  COMPLETED $9,600,000
#>  ...
```

The tour code prefix tells you which tour:

| Code | Tour |
|------|------|
| `R`  | PGA Tour |
| `S`  | PGA Tour Champions |
| `H`  | Korn Ferry Tour |
| `Y`  | PGA Tour Americas |

## Tracking a Live Tournament

The examples below use `tid` from `pga_current_tournament()`. Any known ID works the same way.

### Leaderboard

The leaderboard is the starting point for any tournament. It returns every player in the field with scores, tee times, movement, and official/projected cup ranks.

```{r leaderboard}
lb <- pga_leaderboard(tid)
lb
#> # A tibble: 69 × 20+
#>    player_id first_name last_name position total tee_time             movement_direction
#>    <chr>     <chr>      <chr>     <chr>    <chr> <chr>                <chr>
#>  1 46046     Scottie    Scheffler 1        -11   2026-08-15T17:45:00Z CONSTANT
#>  2 39971     Sungjae    Im        T2       -8    2026-08-15T17:45:00Z UP
#>  ...
```

For a quick snapshot of just the top 15, use `pga_current_leaders()`:

```{r current-leaders}
pga_current_leaders(tid)
```

Hole-by-hole scores for the **entire field**, and the strokes-gained board:

```{r leaderboard-extra}
pga_leaderboard_holes(tid, round = 2)
pga_leaderboard_strokes(tid)
pga_leaderboard_stats(tid)
```

### Field

Who is in the event — including OWGR, withdrawn players, and alternates:

```{r field}
field <- pga_field(tid)
field[, c("display_name", "role", "owgr", "withdrawn", "status")]
#> # A tibble: 69 × 5
#>    display_name      role   owgr  withdrawn status
#>    <chr>             <chr>  <chr> <lgl>     <chr>
#>  1 Scottie Scheffler player 1     FALSE     Uncut
#>  2 Sungjae Im        player 20    FALSE     Uncut
#>  ...

# Course-fit or recent-form splits for the same field
pga_field_stats(tid, "COURSE_FIT")
pga_field_stats(tid, "CURRENT_FORM")
```

### Tee Times

See who's grouped together and when they tee off:

```{r tee-times}
tt <- pga_tee_times(tid)
tt
#> # A tibble: 270 × 12
#>    round_number tee_time            start_tee display_name    group_number
#>           <int> <dttm>                  <int> <chr>                  <int>
#>  1            1 2026-03-19 07:35:00         1 Alex Smalley               1
#>  2            1 2026-03-19 07:35:00         1 Justin Lower               1
#>  3            1 2026-03-19 07:35:00         1 Max McGreevy               1
#>  ...
```

Tee times are returned as proper `POSIXct` timestamps in the tournament's local timezone.

### Tournament Metadata

Get the full picture — name, location, dates, format, snapshot weather:

```{r tournament-meta}
t <- pga_tournaments(tid)
t$tournament_name
#> "FedEx St. Jude Championship"

t$weather_condition
t$weather_temp_f
```

The `courses` column is a list-column of course details. For hub-page copy, defending champions, and course blurbs:

```{r tournament-overview}
ov <- pga_tournament_overview(tid)
ov$overview
ov$champions
ov$courses
```

Hourly and daily forecast (richer than the snapshot on `pga_tournaments()`):

```{r weather}
wx <- pga_weather(tid)
table(wx$scope)
#> daily hourly
#>     7     12
```

### Course stats

Scoring averages, birdie/bogey counts, and rank for each hole, by round. Summary rows (out / in / total) have `is_summary = TRUE`.

```{r course-stats}
cs <- pga_course_stats(tid)
cs[cs$is_summary == FALSE, c("round_header", "hole_number", "par", "yards",
                             "scoring_average", "birdies", "bogeys", "rank")]

# Season hub (hardest / easiest holes, etc.)
pga_course_stats_overview()

# One hole: scoring mix plus who is on it
hd <- pga_hole_details(tid, course_id = "513", hole = 18)
hd$stats
hd$groups
```

Historical field results for a prior playing of the same event (many tournaments have decades of seasons):

```{r past-results}
past <- pga_tournament_past_results(tid, year = 2025)
past[, c("display_name", "position", "total", "to_par")]
```

### Broadcast Schedule

See what's live and what's coming up:

```{r coverage}
pga_coverage(tid)
#> # A tibble: 16 × 7
#>    coverage_type          stream_title            round_number live_status
#>    <chr>                  <chr>                          <int> <chr>
#>  1 BroadcastFullTelecast  Round 1 - Broadcast                1 LIVE
#>  2 BroadcastFullTelecast  Main Feed                          2 UPCOMING
#>  3 BroadcastFeaturedGroup Marquee Group - S. Ry…             2 UPCOMING
#>  ...
```

### Odds

Outright winner lines, then the rest of the book:

```{r odds}
odds <- pga_odds(tid)
odds
#> # A tibble: 70 × 5
#>    player_id odds    odds_sort odds_direction option_id
#>    <chr>     <chr>       <dbl> <chr>          <chr>
#>  1 46046     -220         1.45 UP             ...
#>  ...

# Market catalog: To Win, matchups, finishes, groups, player props, 3-ball
pga_odds_markets(tid)

# Every quoted line for one player
pga_odds_player(tid, "46046")
```

## Player Deep Dive

### Scorecard

Get a player's hole-by-hole results. Each row is one hole in one round:

```{r scorecard}
sc <- pga_scorecard(tid, "46046")
sc
#> # A tibble: 18 × 11
#>    round_number hole_number   par score status yardage round_score
#>           <int>       <int> <int> <chr> <chr>    <int> <chr>
#>  1            1          10     4 3     BIRDIE     437 -1
#>  2            1          11     5 3     EAGLE      561 -3
#>  3            1          12     4 3     BIRDIE     370 -4
#>  ...
```

The `status` column gives you the result on each hole (EAGLE, BIRDIE, PAR, BOGEY, etc.), and `round_score` is the running score relative to par.

Scorecard-adjacent stat splits (strokes gained, scoring) for the same player:

```{r scorecard-stats}
pga_scorecard_stats(tid, "46046")
```

### Shot-Level Tracking

This is the most granular data available — every shot a player hits, with distances, play-by-play descriptions, and coordinate data for visualization:

```{r shot-details}
shots <- pga_shot_details(tid, "46046", round = 1)
shots
#> # A tibble: 65 × 15+
#>    hole_number stroke_number play_by_play                        distance
#>          <int>         <int> <chr>                               <chr>
#>  1          10             1 303 yds to left tree outline, 136…  303 yds
#>  2          10             2 134 yds to left green, 10 ft 2 in… 134 yds
#>  3          10             3 In the hole                         10 ft 2 in.
#>  ...
```

The response includes coordinate columns (prefixed with `leftToRightCoords` and `bottomToTopCoords`) containing `x`, `y`, `tourcastX`, `tourcastY`, and `tourcastZ` values for both the `from` and `to` positions of each stroke. These can be used to plot shot patterns on a course map.

The hole-level shot cloud (every tracked landing spot on one hole):

```{r scatter}
pga_shot_scatter(tid, course = 513, hole = 1)
```

Live group locations on the course:

```{r group-locations}
pga_group_locations(tid, round = 3)
```

### Video Highlights

Get video clips for a specific player in a tournament:

```{r videos}
pga_videos(player_ids = "46046", tournament_id = "027")
#> # A tibble: 18 × 17
#>    title                                  duration_secs hole_number pub_date
#>    <chr>                                          <int> <chr>       <dttm>
#>  1 Sungjae Im hits 117-yard approach to…             25 5           2026-03-19 16:42:12
#>  2 Sungjae Im sinks 44-foot birdie putt…             16 3           2026-03-19 16:05:19
#>  ...
```

Note: `pga_videos()` takes the numeric tournament ID (`"027"`) without the tour/year prefix, while most other functions use the full ID (`"R2026027"`).

For shot-by-shot video clips (one clip per stroke in a round):

```{r tourcast}
pga_tourcast_videos(tid, "46046", round = 1)
```

## Player Profiles

The player profile endpoints give you a deep dive on any player — all from REST endpoints that don't require GraphQL.

### Profile Overview

```{r player-profile}
profile <- pga_player_profile("52955")  # Ludvig Aberg
profile$first_name   # "Ludvig"
profile$country      # "Sweden"
profile$age          # "26"
profile$college      # "Texas Tech University"

# Career highlights: wins, FedExCup rank, world rank
profile$highlights
#> # A tibble: 6 × 3
#>    title                   value subtitle
#>    <chr>                   <chr> <chr>
#>  1 PGA TOUR Wins           2     NA
#>  2 Wins (2026)             0     NA
#>  3 FedExCup Standings      11    PTS: 685
#>  4 World Rank (OWGR)       17    NA
#>  ...

# Quick overview stats (career, season, bio, performance)
profile$overview
```

### Player Stats (131 Stats in One Call)

This is one of the most powerful endpoints — a player's full stat profile with ranks:

```{r player-stats}
stats <- pga_player_stats("52955")
#> # A tibble: 131 × 11
#>    stat_id title                rank  value  category
#>    <chr>   <chr>                <chr> <chr>  <chr>
#>  1 02675   SG: Total            13    1.245  STROKES_GAINED, SCORING
#>  2 02674   SG: Tee-to-Green     12    1.150  STROKES_GAINED, DRIVING
#>  3 02567   SG: Off-the-Tee      29    0.460  STROKES_GAINED, DRIVING
#>  4 02568   SG: Approach the Gr… 23    0.508  STROKES_GAINED, APPROACH
#>  ...
```

### Tournament Results

```{r player-results}
results <- pga_player_results("52955")
results[, c("tournament", "pos", "total", "to_par", "winnings")]
#> # A tibble: 6 × 5
#>    tournament                 pos   total to_par winnings
#>    <chr>                      <chr> <chr> <chr>  <chr>
#>  1 The American Express       W/D   135   -9     $-
#>  2 Farmers Insurance Open     CUT   150   +6     $-
#>  3 AT&T Pebble Beach Pro-Am   T37   277   -11    $78,375
#>  4 The Genesis Invitational   T20   275   -9     $259,500
#>  5 Arnold Palmer Invitational T3    276   -12    $1,200,000
#>  6 THE PLAYERS Championship   T5    279   -9     $925,000
```

### Career, Bio, and Tournament Status

```{r player-other}
# Career achievements
pga_player_career("52955")

# Biographical text and amateur highlights
bio <- pga_player_bio("52955")
bio$text  # Character vector of bio paragraphs
length(bio$amateur_highlights)  # 19 amateur achievements

# Is a player in the current tournament?
pga_player_tournament_status("46046")
#> # A tibble: 1 × 11
#>    player_id tournament_name               position thru  score total
#>    <chr>     <chr>                         <chr>    <chr> <chr> <chr>
#>  1 46046     FedEx St. Jude Championship   1        F     -11   -11

# One stat across recent starts
pga_player_finish_stats("46046", "02675")
```

## Statistics

### Pulling Stats

pgatouR gives you access to 470+ PGA Tour statistics going back to 2004. Every stat has a unique ID:

```{r stats-basic}
# Strokes Gained: Total
sg <- pga_stats("02675")
sg
#> # A tibble: 195 × 7+
#>     rank player_name       country          ...
#>    <int> <chr>             <chr>            ...
#>  1     1 Jacob Bridgeman   United States    ...
#>  2     2 Jake Knapp        United States    ...
#>  3     3 Scottie Scheffler United States    ...
#>  ...
```

`stat_id`, `year`, and `stat_title` are real columns on the tibble (not attributes), so they survive dplyr verbs.

### Finding Stat IDs

The package includes a bundled `stat_ids` dataset with 470+ known stat IDs. `pga_stat_catalog()` pulls the same tree live from the stats hub if you want newly published IDs:

```{r stat-ids-browse}
# All strokes gained stats
stat_ids[stat_ids$category == "Strokes Gained", ]
#> # A tibble: 6 × 4
#>   stat_id stat_name              category       subcategory
#>   <chr>   <chr>                  <chr>          <chr>
#> 1 02675   SG: Total              Strokes Gained Strokes Gained Leaders
#> 2 02674   SG: Tee-to-Green       Strokes Gained Strokes Gained Leaders
#> 3 02567   SG: Off-the-Tee        Strokes Gained Strokes Gained Leaders
#> 4 02568   SG: Approach the Green Strokes Gained Strokes Gained Leaders
#> 5 02569   SG: Around-the-Green   Strokes Gained Strokes Gained Leaders
#> 6 02564   SG: Putting            Strokes Gained Strokes Gained Leaders

# Search by name
stat_ids[grep("Driving Distance", stat_ids$stat_name), ]

# See all categories
unique(stat_ids$category)
#> "Strokes Gained"    "Off The Tee"       "Approach the Green"
#> "Around the Green"  "Putting"           "Scoring"
#> "Streaks"           "Money/Finishes"    "Points/Rankings"

# Live hub catalog + featured leaders
pga_stat_catalog()
pga_stat_leaders()
```

### Historical Comparisons

Pull the same stat across multiple years:

```{r stats-historical}
dd_2026 <- pga_stats("101", year = 2026)  # Driving Distance
dd_2020 <- pga_stats("101", year = 2020)
dd_2015 <- pga_stats("101", year = 2015)
```

### Common Stat IDs

Here are the ones you'll probably use most:

| Stat ID | Stat |
|---------|------|
| `02675` | SG: Total |
| `02674` | SG: Tee-to-Green |
| `02567` | SG: Off-the-Tee |
| `02568` | SG: Approach the Green |
| `02569` | SG: Around-the-Green |
| `02564` | SG: Putting |
| `101`   | Driving Distance |
| `102`   | Driving Accuracy Percentage |
| `103`   | Greens in Regulation Percentage |
| `130`   | Scrambling |
| `104`   | Putting Average |
| `120`   | Scoring Average (Adjusted) |

## Season Schedule

Get the full season schedule with dates, purse, course info, champions, and FedExCup points:

```{r schedule}
schedule <- pga_schedule(2026)
schedule
#> # A tibble: 49 × 15
#>    tournament_id tournament_name       display_date status    purse
#>    <chr>         <chr>                 <chr>        <chr>     <chr>
#>  1 R2026006      Sony Open in Hawaii   Jan 15 - 18  COMPLETED $9,100,000
#>  2 R2026002      The American Express  Jan 22 - 25  COMPLETED $9,200,000
#>  ...

# See champions and earnings for completed events
schedule[schedule$status == "COMPLETED",
         c("tournament_name", "champion", "champion_earnings")]

# Use tournament IDs with other functions
pga_leaderboard("R2026006")

# Past seasons work too
pga_schedule(2025)
```

## Standings

### FedExCup

```{r fedex}
fc <- pga_fedex_cup(2026)
fc
#> # A tibble: 192 × 14
#>    display_name      this_week_rank projected_points ...
#>    <chr>             <chr>          <chr>            ...
#>  1 Jacob Bridgeman   1              1,403.981        ...
#>  2 Cameron Young     2              1,323.014        ...
#>  3 Akshay Bhatia     3              1,224.306        ...
#>  ...
```

`pga_cup_standings()` is the simpler table and picks the right cup for the tour (FedExCup, Schwab, Fortinet, Americas points):

```{r cup-standings}
pga_cup_standings(2026)
pga_cup_standings(2026, tour = "H")
```

Playoff / tour-card bubble around the cutoff, when the API is publishing one:

```{r bubble}
pga_bubble(tid)
```

### Signature events and priority rankings

```{r signature-priority}
# Aon / signature-event official and interim tables
pga_signature_standings()

# Exemption categories (winners of majors, career money, …)
pr <- pga_priority_rankings(year = 2026)
unique(pr$category)
```

### University and all-time records

```{r records}
pga_university_rankings(year = 2026)

cats <- pga_all_time_record_categories()
pga_all_time_records(cats$record_id[1])
```

## Player Directory

The full player directory has 2,700+ players on the PGA Tour (plus Champions, Korn Ferry, and Americas):

```{r players}
players <- pga_players("R")
nrow(players)
#> 2737

# Filter to active players
active <- players[players$is_active, ]
nrow(active)

# Other tours
champions  <- pga_players("S")
korn_ferry <- pga_players("H")
americas   <- pga_players("Y")
```

## News

```{r news}
# Latest articles
news <- pga_news(limit = 10)
news[, c("headline", "publish_date", "franchise_display_name")]

# See available categories
pga_news_franchises()
#> # A tibble: 7 × 2
#>   franchise        franchise_label
#>   <chr>            <chr>
#> 1 latest           Latest
#> 2 power-rankings   Power Rankings
#> 3 expert-picks     Expert Picks
#> 4 equipment-report Equipment
#> 5 tour-insider     Tour Insider
#> 6 needtoknow       Need to Know
#> 7 daily-wrapup     Daily Wrap Up

# Filter by category
pga_news(franchises = "power-rankings", limit = 5)
```

## Tips

- **This week's ID:** `pga_current_tournament()` is the same source the live site uses. Pass `"S"`, `"H"`, or `"Y"` for the other tours.
- **Rate limiting** is built in at 10 requests/second. You don't need to add delays.
- **Compressed payloads** (leaderboards, scorecards, tee times, shot details, odds, scatter, scorecard stats) are decompressed automatically. You always get a clean tibble.
- **Error messages** use the cli package and will tell you exactly what went wrong (bad tournament ID, API errors, etc.).
- **`stat_ids`** is lazy-loaded — just type `stat_ids` to access it, no `data()` call needed. Use `pga_stat_catalog()` when you want the live hub instead of the bundled snapshot.
- The **`@return`** section in each function's help page (`?pga_leaderboard`) describes the exact columns you'll get back.
